Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-14 paper/sections/implementation.tex
[ paper ] improving minor texts.

In \Agda, we define a proposition formula
as an inductive type using the keyword \texttt{data} extending the
its definition in \cite{Altenkirch2015}.
The \name{PropFormula} data type stands for propositions
as we define in section \ref{sec:preliminaries}.
We include every connective and logic constant as a constructor.
We also define the constructor for atomic propositions denoted by
\verb!Var!. These atomic expressions are represented using a natural
number $i$ bounded by a size of the universe $n$ for those atomic
propositions (in \Agda, we use the data type \verb!Fin! from the
standard  library for such a purpose).

>>>>

In \Agda, we have defined a proposition formula
as an inductive type using the keyword \texttt{data} and the name
\name{PropFormula}.
We extended the definition for propositions presented in
\cite{Altenkirch2015} to mathc the definion in section
\ref{sec:preliminaries}.
We include every connective and logic constant as a constructor.
We also define the constructor for atomic propositions denoted by
\verb!Var!. These atomic expressions are represented using a natural
number $i$ bounded by a size of the universe $n$ for those atomic
propositions (in \Agda, we use the data type \verb!Fin! from the
standard  library for such a purpose).

### 2017-09-14 paper/sections/proof-reconstruction.tex
[ paper ] improving minor texts.

To rearrange the proposition in order to match with a specific
pattern of a formula, we define the following functions and provide
its respective theorems in \cite{AgdaMetis}.

\begin{itemize}
  \item[] \name{reorder-∨}
  \item[] \name{reorder-∧}
  \item[] \name{reorder-∧∨}
\end{itemize}

>>>>

To rearrange the propositions in order to match with a specific
pattern for applying a particular theorem like resolution, we have
define the following functions and provide
its respective theorems in \cite{AgdaMetis}.
These rearrangement functions are mainly inspired in
\cite{bohme2010}, for their treatment for conjunction and
disjunction equivalence.

\improvement{provide examples for each of the following functions.}

\begin{itemize}
  \item \name{reorder-∨.} Given two formulas, φ and ψ, both disjunctions, fix the order of the first one by following the syntactically
  order of the second one. If the process succeed (denote by φ ⤳ ψ),
  returns the target formula, ψ, otherwise, keep the first one, φ.
  \begin{align}
  \begin{split}
&\name{reorder-∨}\ :\ \PROP \to \PROP \to \PROP\\
&\name{reorder-∨}(φ, ψ) =
  \begin{cases}
  ψ   & φ ⤳ ψ\\
  ϕ   & \text{otherwise.}
  \end{cases}
  \end{split}
  \end{align}

  \item \name{reorder-∧.} Given two formulas, φ and ψ, both conjunctions, fix the order of the first one by following the order  of the second one.
  \item \name{reorder-∧∨.} Given two formulas, φ and ψ, both in CNF, fix the order of the first one by following the order  of the second one.
\end{itemize}
